Bayesian phylogenetic estimation of fossil ages

### 2016-01-27 fossilDating.tex
changes for arXiv submission

% !BIB TS-program = biber
\documentclass[11pt]{article}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage[style=authoryear,backend=biber,mincitenames=1,maxcitenames=2, uniquelist=false]{biblatex}
\bibliography{fossilDating.bib}

@@

\begin{figure}
\includegraphics[width=6in]{8_penguins_eNprior/8_fossilDatingHist_younger.pdf}
\caption{\label{hist8_younger}Marginal posterior density plots for the phylogenetic age estimate of each of the 18 penguin fossils younger than 30 Myr using \Mrelaxed{}. Red boxes are the superimposed age ranges derived from geological data.}
\end{figure}

\begin{figure}
\includegraphics[width=6in]{8_penguins_eNprior/8_fossilDatingHist_older.pdf}
\caption{\label{hist8_older}Marginal posterior density plots for the phylogenetic age estimate of each of the 18 penguin fossils older than 30 Myr using \Mrelaxed{}. Red boxes are the superimposed age ranges derived from geological data.}
\end{figure}

@@

\input{1_penguins_eNprior/1_summaryTable.tex}

\input{8_penguins_eNprior/8_summaryTable.tex}

@@

\begin{figure}
\includegraphics{canids/1c_phyloAgeVsGeoAge.pdf}
\caption{\label{fig:canidMorphVsGeo}
The Bayesian phylogenetic age estimate (median and credible interval of marginal posterior) for each of the 123 canid fossils plotted against their palaeontological age point estimates, under a strict morphological clock model \Mstrict{}. 
The Bayesian estimates are represented by the median of the marginal posterior distribution and the upper and lower limits of the 99\% HPD interval. Blue line shows the $x=y$. 
If the vertical line doesn't cross $x=y$, then the geological age is not in the credible interval of the phylogenetic age. The 16 fossils for which this is the case are labelled.}
%TS I find this plot very hard to read as many fossils are overlaying...can we do something there for better visualization?
\end{figure}

\begin{figure}
\includegraphics[width=15cm]{canids/1_canids-1440516016976-tree5001.pdf}
\caption{\label{fig:canidTree} A sample from the posterior distribution of an analysis of the canid data set, showing two main clades, one containing the extant taxa and another constituted entirely of extinct fossil species.}
\end{figure}

>>>>

\documentclass[11pt]{article}

\usepackage{graphicx}
%\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage[style=authoryear,backend=bibtex,mincitenames=1,maxcitenames=2, uniquelist=false]{biblatex}
\bibliography{fossilDating.bib}

@@

\begin{figure}
\includegraphics[width=6in]{8_fossilDatingHist_younger.pdf}
\caption{\label{hist8_younger}Marginal posterior density plots for the phylogenetic age estimate of each of the 18 penguin fossils younger than 30 Myr using \Mrelaxed{}. Red boxes are the superimposed age ranges derived from geological data.}
\end{figure}

\begin{figure}
\includegraphics[width=6in]{8_fossilDatingHist_older.pdf}
\caption{\label{hist8_older}Marginal posterior density plots for the phylogenetic age estimate of each of the 18 penguin fossils older than 30 Myr using \Mrelaxed{}. Red boxes are the superimposed age ranges derived from geological data.}
\end{figure}

@@

\input{1_summaryTable.tex}

\input{8_summaryTable.tex}

@@

\begin{figure}
\includegraphics{1c_phyloAgeVsGeoAge.pdf}
\caption{\label{fig:canidMorphVsGeo}
The Bayesian phylogenetic age estimate (median and credible interval of marginal posterior) for each of the 123 canid fossils plotted against their palaeontological age point estimates, under a strict morphological clock model \Mstrict{}. 
The Bayesian estimates are represented by the median of the marginal posterior distribution and the upper and lower limits of the 99\% HPD interval. Blue line shows the $x=y$. 
If the vertical line doesn't cross $x=y$, then the geological age is not in the credible interval of the phylogenetic age. The 16 fossils for which this is the case are labelled.}
%TS I find this plot very hard to read as many fossils are overlaying...can we do something there for better visualization?
\end{figure}

\begin{figure}
\includegraphics[width=15cm]{1_canids-1440516016976-tree5001.pdf}
\caption{\label{fig:canidTree} A sample from the posterior distribution of an analysis of the canid data set, showing two main clades, one containing the extant taxa and another constituted entirely of extinct fossil species.}
\end{figure}
